%-----------------------------------------------------------------------------------------------------
% AUTHOR: Soumitra Samanta (soumitra.samanta@gm.rkmvu.ac.in)
%-----------------------------------------------------------------------------------------------------

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{color}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\usepackage{hyperref} 

%SetFonts

%SetFonts

\title{Your project title}
\author{Group name\\
Your name}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\section*{Abstract}

Project summary in 8-10 sentences (max 100 words).

\section{Introduction}
A brief description of your project (you should explain about your project to answer what?, why? and how?) with some literature survey.

\section{Proposed methodology}
Here is your proposed method to tackle the above problem. 

\section{Work plan and time line}

You should mention a time line for different parts of your project. Something like \href{https://en.wikipedia.org/wiki/Gantt_chart}{Gantt chart}, you can use Excel to draw your Gantt chart~\url{https://support.microsoft.com/en-us/office/present-your-data-in-a-gantt-chart-in-excel-f8910ab4-ceda-4521-8207-f0fb34d9e2b6} 


\section{Work plan division in your group}

Who will do what in your project?

\section{References}

Some references related to your project. I am attaching a \textit{ml\_reference.bib} file and you can use that. You have to add your \textit{bibtex} according to your references {like conference, journal, book, etc.}. Your reference section should be some like bellow:


\nocite{*}% Biblography without citation!
	
\bibliography{ml_reference} % .bib file
\bibliographystyle{plain}


\end{document}  